A Topic Model of Climate Change Literature

### 2018-11-27 main.tex

<<<<<<< HEAD
\documentclass{article}
\usepackage[a4paper, total={6in, 8in}]{geometry}
\usepackage{graphicx}
\usepackage{url}
\usepackage{natbib}
\usepackage{todonotes}
\usepackage{booktabs}
\usepackage{lineno}
\usepackage{color}
%\usepackage{auto-pst-pdf}
\usepackage[colaction]{multicol}
\usepackage{caption}
\usepackage{svg}
\usepackage{authblk}

@@

=======
\documentclass{article}
\usepackage[a4paper, total={6in, 8in}]{geometry}
\usepackage{graphicx}
\usepackage{url}
\usepackage{natbib}
\usepackage{todonotes}
\usepackage{booktabs}
\usepackage{lineno}
\usepackage{color}
\usepackage{auto-pst-pdf}
\usepackage[colaction]{multicol}
\usepackage{caption}
\usepackage{svg}
\usepackage{authblk}

\begin{figure}
	\begin{center}
		\includegraphics[width=0.5\linewidth]{plots/literature_size/volume_variety.pdf}
		%\captionof{figure}
		\caption{The volume and variety of literature on climate change has grown to unmanageable proportions. Each box represents a document-term matrix (unique documents x unique terms) of the abstracts written in each assessment period. The percentage of documents in which the average word occurs in is given in the key.
		}
		\label{growth}
	\end{center}
\end{figure}

\begin{figure}
	\begin{center}
		\includegraphics[width=1\linewidth]{plots/tsne.png}
		\caption{A map of a sample of 10,000 documents about climate change. Document positions are obtained by reducing the topic scores to two dimensions via t-SNE}
		\label{}
	\end{center}
\end{figure}

\begin{figure}
	\begin{center}
		\includegraphics[width=1\linewidth]{plots/network_development_wgs_665.pdf}
		\caption{The development of the topic-document correlation network over IPCC assessment periods.}
		\label{}
	\end{center}
\end{figure}

>>>>>>> 0261e7b8054b72195fb991f1ca7947fd5b9a6b9d

>>>>

\documentclass{article}
\usepackage[a4paper, total={6in, 8in}]{geometry}
\usepackage{graphicx}
\usepackage{url}
\usepackage{natbib}
\usepackage{todonotes}
\usepackage{booktabs}
\usepackage{lineno}
\usepackage{color}
%\usepackage{auto-pst-pdf}
\usepackage[colaction]{multicol}
\usepackage{caption}
\usepackage{svg}
\usepackage{authblk}

@@
